Verifying Demonstrations

### 2017-08-25 security.tex
Fixes typo
adds section on spoofing locations, just stub
Adds stuff to security section

@@

\subsubsection{Forging new proofs}

@@

The Eve (possibly with Rusuk's aid) wants to arrange a counter-protest in Eve's 
favour.
One way to get a higher participation count is to use the same identifier as 
Alice's protest.
Since the identifier for the protest is the hash value of the manifest, Eve 
must find a second preimage for the hash function.

@@

>>>>

\subsection{Forging new proofs}

It follows from the digital signatures used that proofs are difficult to forge.

@@

@@

Eve (possibly with Rusuk's aid) wants to arrange a counter-protest.
One way to get a higher participation count is to use the same identifier as 
Alice's protest.
Since the identifier for the protest is the hash value of the manifest, Eve 
must find a second preimage for the hash function.

@@

Alice wants to arrange another protest against Eve.
Her manifesto can remain the same, thus the protest identifier remains the 
same.
She wants to reuse some old proofs.
The head value that are included in the proofs extend them too far back into 
time.
The digital signatures prevents her from changing them.
So an alternative is to create nodes in the \ac{tposet} which has the same 
hashes.

\subsection{Spoofing locations}

\subsubsection{Trust propagation for witnesses}

\subsection{Individual verifiability}

Eve and Rusuk has an incentive to lower the confidence in the result.
One way they can do this is to say that the result does not contain all 
participation proofs.
Statements such as this should be proved: provide a valid but missing proof.
